beautier: BEAUti for R

### 2017-12-29 article.tex
EOD

\begin{lstlisting}[language=R, caption=Example with fixed crown age, label=lst:fixed_crown_age, floatplacement=H]
create_beast2_input_file(
  "alignment.fas",
  "beast2.xml"
  crown_age = 15
)
\end{lstlisting}

>>>>

\begin{lstlisting}[language=R, caption=Example with fixed crown age, label=lst:fixed_crown_age, floatplacement=H]
create_beast2_input_file(
  "alignment.fas",
  "beast2.xml"
  posterior_crown_age = 15
)
\end{lstlisting}
